---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 6,
  fig.height = 4
)
```

# msepBoundaries

<!-- badges: start -->
<!-- badges: end -->

The `msepBoundaries` package is a collection of several spatial data frames delineating Mississippi Sound Estuary Program (MSEP) boundaries in different ways.  


## Installation

You can install the development version of msepBoundaries from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("CMEP-MS/msepBoundaries")
```

## Examples  

Here are a couple of examples. First load the libraries:  

```{r libraries}
library(msepBoundaries)
library(ggplot2)
library(dplyr)
library(tigris)
options(tigris_use_cache = TRUE)
lamsal <- states(cb = TRUE) |> 
    filter(NAME %in% c("Mississippi", "Alabama", "Louisiana"))
```

### Full Outline  

The outline of the entire watershed.  

```{r}
ggplot() +
    geom_sf(data = outline_full,
            fill = "blue",
            alpha = 0.5) +
    geom_sf(data = lamsal,
            fill = NA) +
    theme_void()
```


### Subbasins  

Subbasins (HUC8) for the entire watershed.

The outline of the entire watershed.  

```{r}
ggplot() +
    geom_sf(data = subbasins_full,
            aes(fill = name),
            alpha = 0.5) +
    geom_sf(data = lamsal,
            fill = NA) +
    theme_void()
```

### Land-only subbasins, and only Mississippi  

In case we want to ignore the large area of water that is the Mississippi Sound, and restrict the area to the state of Mississippi.  

```{r}
ggplot() +
    geom_sf(data = subbasins_ms_land,
            aes(fill = name),
            alpha = 0.5) +
    geom_sf(data = lamsal,
            fill = NA) +
    theme_void()
```
