---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 6,
  fig.height = 5,
  message = FALSE,
  warning = FALSE
)
```

# msepBoundaries

<!-- badges: start -->
<!-- badges: end -->

The `msepBoundaries` package is a collection of several spatial data frames delineating Mississippi Sound Estuary Program (MSEP) boundaries in different ways.  


## Installation

You can install the development version of msepBoundaries from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("CMEP-MS/msepBoundaries")
```

## Contents  

`msepBoundaries` currently contains 8 spatial data frames. They are various combinations of:  

-  Outline, as the combination of HUC4 units 0317 and 0318 ("outline") vs. Subbasins, which are the HUC8s contained in those HUC4s ("subbasins").  
-  Entire region ("full") vs. the region excluding the Mississippi Sound itself ("land").  
-  Entire watershed vs. only within the state of Mississippi ("_ms_").  

So `outline_full` contains everything. `outline_land` contains everything except the Mississippi Sound. `outline_ms_full` contains everything within the state of MS. `outline_ms_land` is that, but without the Mississippi Sound itself. Data frames starting with `subbasins` follow the same pattern, but are split into HUC8s.  

## What it looks like  

Here are a couple of examples. First load the libraries and use `{tigris}` to get state outlines (`{tigris}` uses boundary data from the US Census Bureau):  

```{r libraries, warning = FALSE, message = FALSE}
library(msepBoundaries)
library(dplyr)
library(tigris)
options(tigris_use_cache = TRUE)
library(ggplot2)

# get the outlines of MS, AL, and LA
lamsal <- states(cb = TRUE) |> 
    filter(NAME %in% c("Mississippi", "Alabama", "Louisiana"))
```

### Full Outline  

The outline of the entire watershed.  

```{r, fig.width = 5, fig.height = 4.5}
ggplot() +
    geom_sf(data = outline_full,
            fill = "blue",
            alpha = 0.6) +
    geom_sf(data = lamsal,
            fill = NA) +
    theme_void() +
    ggtitle("Full watershed")
```


### Subbasins  

Subbasins (HUC8) for the entire watershed.


```{r}
ggplot() +
    geom_sf(data = subbasins_full,
            aes(fill = name),
            alpha = 0.7) +
    geom_sf(data = lamsal,
            fill = NA) +
    scale_fill_viridis_d() +
    theme_void() +
    labs(title = "Full watershed",
         fill = "Subbasin")
```



### Land-only subbasins, and only Mississippi  

In case we want to ignore the large area of water that is the Mississippi Sound, and restrict the area to the state of Mississippi.  

```{r}
ggplot() +
    geom_sf(data = subbasins_ms_land,
            aes(fill = name),
            alpha = 0.7) +
    geom_sf(data = lamsal,
            fill = NA) +
    theme_void() +
    scale_fill_viridis_d() +
    labs(title = "MS-only, cartographic boundaries",
         fill = "Subbasin")
```

